\section{Competitors Analysis}
After analyzing two similar services, \href{https://www.life360.com}{Life360} and \href{https://findmykids.org}{Find My Kids}, we have gained valuable insights into their features and functionalities. Enhancing our understanding of these competitors allows us to refine our mobile application's goals and better align them with user expectations.

\subsection{Life360}
Life360 is a comprehensive location-sharing and communication platform for families and friends. It utilizes GPS technology to track designated group members' real-time location and share it with others. In addition, the app offers driving safety alerts, crash detection, emergency response, location history, and a communication platform for better coordination. While it provides valuable features for family safety and connectivity, privacy concerns, battery drain, and limited functionality \footnote{Advanced features are only available for subscribed users.} are some drawbacks to consider.

\subsection{Find My Kids}
On the other hand, Find My Kids specifically targets parents seeking to ensure their children's safety. It offers real-time location tracking, geofencing\footnote{Geofencing is a technology that creates virtual boundaries in the real world, and GPS, Wi-Fi, or RFID triggers actions or notifications when a device enters or exits these boundaries.} to set up safe zones and panic alerts in emergencies. The app aims to give parents peace of mind and assist in keeping their children safe. However, privacy concerns, false alarms, battery drain, limited functionality, and potential costs are factors to consider.